---
title: "Practical machine learning"
output:
  html_document: default
---


## Synopsis

The goal of this project is to predict the manner in which people did the 
barebell lifts using data from accelerometers on the belt, forearm, arm, and 
dumbell of 6 participants. 


## Data preprocessing
```{r}
download.file(
    "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv",
    destfile = "data/pml-training.csv", method = "curl")

download.file(
    "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv",
    destfile = "data/pml-testing.csv", method = "curl")

raw_train <- read.csv("data/pml-training.csv", 
                      na.strings= c("NA",""," ", "#DIV/0!"))
raw_test <- read.csv("data/pml-testing.csv", 
                     na.strings = c("NA", "", " ", "#DIV/0!"))
```

Remove columns with NA values and split raw_train on train and cross validation data sets
```{r}
library(caret)

NAcnt <- apply(raw_train, 2, function(x) {sum(is.na(x))} )  
is_train <- createDataPartition(y = raw_train$classe, p=0.7, list = FALSE)
ds_train <- raw_train[is_train, NAcnt == 0]
ds_cv <- raw_train[-is_train, NAcnt == 0]
ds_test <- raw_test[, NAcnt == 0]
```

## Train model

Train random forest model with custom train control function

```{r}
   trctr <- trainControl(method = "cv", number = 4)
   mdl <- train(classe ~ ., data = ds_train, method = "rf", trControl = trctr)
```

## Prediction

```{r}
ds_prdct <- predict(mdl, ds_cv)
smpl_err <- sum(ds_cv$classe == ds_prdct)/nrow(ds_cv)
```
Sample error is `r smpl_err`.